CKY Parsing With Independence Constraints

### 2015-07-14 paper.tex
Move table
Make equations in appendix smaller
Fix problems with format
- papersize somehow was US Letter
- margins were wrong because of ↑
- appendices should come after references
- appendix title should begin with "Appendix"
Fix table(s) to fit content in 9 pages

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{acl2015}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{forest}
\usepackage[linesnumbered]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\BigO}[1]{\ensuremath{\operatorname{O}\bigl(#1\bigr)}}
\newcommand{\Dag}{\ensuremath{^{\dagger}}}

@@

@@

We use only part-of-speech tags to create features for the classifier
(adding lexical or other features is left to future work). The
property of independence between two words is inherently global, as it
can be affected by structure arbitrarily far away. Thus we have both
local and global features. The global features are furthermore
distinguished by \textbf{POS level}, explained in detail later. The specific
feature templates are shown below:

\subsubsection{Local Features}
\label{sec-4-1-1}
\begin{enumerate}
\item Left
\label{sec-4-1-1-1}
\begin{itemize}
\item $t_{k-1}$
\item $t_{k-2},t_{k-1}$
\item $t_{k-3},t_{k-2},t_{k-1}$
\end{itemize}

\item Right
\label{sec-4-1-1-2}
\begin{itemize}
\item $t_{k}$
\item $t_{k},t_{k+1}$
\item $t_{k},t_{k+1},t_{k+2}$
\end{itemize}
\end{enumerate}

\subsubsection{Global Features}
\label{sec-4-1-2}

Below, $t^{l}_{i}$ is the $i$ th POS tag in the $l$-level POS tag sequence.

\begin{enumerate}
\item Left
\label{sec-4-1-2-1}
\begin{itemize}
\item $t^l_{i}$ for $1 \le i < k - 1$, $l \in {0,1,2,3}$
\item $t^l_{i},t^l_{i+1}$ for $1 \le i < k - 2$, $l \in {0,1,2,3}$
\item $t^l_{i},t^l_{i+1},t^l_{i+2}$ for $1 \le i < k - 3$, $l \in {0,1,2,3}$
\end{itemize}

\item Right
\label{sec-4-1-2-2}
\begin{itemize}
\item $t^l_{i}$ for $k \le i < n - 1$, $l \in {0,1,2,3}$
\item $t^l_{i},t^l_{i+1}$ for $k \le i < n - 2$, $l \in {0,1,2,3}$
\item $t^l_{i},t^l_{i+1},t^l_{i+2}$ for $k \le i < n - 3$, $l \in {0,1,2,3}$
\end{itemize}
\end{enumerate}

@@

To compare with previous work on parsing using the Penn Treebank, we show the
time and accuracy for parsing section 23, using both linear and kernel
classifier output, along with the baseline parser, below. The times reported are
the average of three runs each. Because there was significant variation in parse
time when multiple processes were run in parallel, for these results only one
process was run at a time. The results parallel those shown on the development
data.

\begin{center}
\begin{tabular}{llll}
{\bf Parser} & {\bf Time} (s) & {\bf Speedup} & {\bf F$_{\text{1}}$} \\
%\hline
baseline & 1538 & & 85.54 \\
linear & 1106 & 1.39\texttimes{} & 83.55 (-1.99)\\
 & (+100) & (1.28\texttimes{}) &  \\
poly & 1040 & 1.48\texttimes{} & 84.57 (-0.97)\\
\end{tabular}
\end{center}

@@

\appendix
%% \section{Appendix}
\label{sec-8}

\section{Derivation of equations in section \ref{sec:comp-saved}}
\label{sec:derivation-equations}

@@

\begin{align*}
%% \begin{equation*}
%% \begin{split}
& \sum_{j=2}^{n}\sum_{i=1}^{n-j+1}\sum_{k=i+1}^{i+j-1}|G|\\
=& |G|\sum_{j=2}^{n}(n-j+1)(j-1)\\
=& |G|\sum_{i=1}^{n-1}(n-i)(i)\\
=& |G|\sum_{i=1}^{n-1}(ni - i^2)\\
=& |G|(n\sum_{i=1}^{n-1}i - \sum_{i=1}^{n-1}i^2)\\
=& |G|(n\frac{(n-1)n}{2} - (\frac{n^3}{3} - \frac{n^2}{2} + \frac{n}{6}))\\
=& |G|(\frac{1}{2}n^3 - \frac{1}{2}n^2 - \frac{1}{3}n^3 + \frac{1}{2}n^2 - \frac{1}{6}n)\\
=& |G|(\frac{1}{6}n^3 - \frac{1}{6}n)
%% \end{split}
%% \end{equation*}
\end{align*}

@@

\begin{equation*}
\begin{split}
& |G_{comp}|[\frac{1}{6}n^3 - \frac{1}{6}n]\\& - |G_{comp}|[\frac{1}{6}(\frac{n}{K})^3 - \frac{1}{6}\frac{n}{K}]\\& - |G_{comp}|[\frac{1}{6}(\frac{(K-1)n}{K})^3 - \frac{1}{6}\frac{(K-1)n}{K}]\\
=& |G_{comp}|[\frac{1}{6}n^3 - \frac{1}{6}n - \frac{1}{6}\frac{(K-1)^3 +1}{K^3}n^3 + \frac{1}{6}n]\\
=& |G_{comp}|[\frac{1}{6}\frac{K^3}{K^3}n^3 - \frac{1}{6}\frac{K^3 - 3K^2 + 3K}{K^3}n^3]\\
=& |G_{comp}|\frac{3K^2 - 3K}{6K^3}n^3
\end{split}
\end{equation*}

@@

\begin{equation*}
\frac{|G_{comp}|\frac{3K^2 - 3K}{6K^3}n^3}{|G|(\frac{1}{6}n^3 - \frac{1}{6}n)}
\end{equation*}

@@

\begin{equation*}
\begin{split}
& \lim_{n \to \infty}\frac{|G_{comp}|\frac{3K^2 - 3K}{6K^3}n^3}{|G|(\frac{1}{6}n^3 - \frac{1}{6}n)}\\
=& \frac{|G_{comp}|}{|G|}[\frac{3}{K} - \frac{3}{K^2}]
\end{split}
\end{equation*}

@@

\begin{equation*}
\begin{split}
& |G_{comp}|[\frac{1}{6}n^3 - \frac{1}{6}n]\\
& - K|G_{comp}|[\frac{1}{6}(\frac{n}{K})^3 - \frac{1}{6}\frac{n}{K}]\\
=& |G_{comp}|[\frac{1}{6}n^3 - \frac{1}{6}n - \frac{1}{6}\frac{1}{K^2}n^3 + \frac{1}{6}\frac{n}{K}]\\
=& |G_{comp}|\frac{1}{6}\frac{K^2-1}{K^2}n^3
\end{split}
\end{equation*}

@@

\begin{equation*}
\begin{split}
& \lim_{n \to \infty}\frac{|G_{comp}|\frac{1}{6}\frac{K^2-1}{K^2}n^3}{|G|(\frac{1}{6}n^3 - \frac{1}{6}n)}\\
=& \frac{|G_{comp}|}{|G|}\frac{K^2-1}{K^2}
\end{split}
\end{equation*}

\section{Detailed parse results}
\label{sec:parse-results-full}
\label{sec-8-2}

@@

\bibliographystyle{acl}
\bibliography{references}
\end{document}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{acl2015}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{forest}
\usepackage[title]{appendix}
\usepackage[linesnumbered]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\BigO}[1]{\ensuremath{\operatorname{O}\bigl(#1\bigr)}}
\newcommand{\Dag}{\ensuremath{^{\dagger}}}

@@

\begin{table}[t]
  \centering
\begin{tabular}{ll}
 \multicolumn{2}{c}{\bf Local Features} \\
 \hline
 $t_{k-1}$                 & $t_{k}$                 \\
 $t_{k-2},t_{k-1}$         & $t_{k},t_{k+1}$         \\
 $t_{k-3},t_{k-2},t_{k-1}$ & $t_{k},t_{k+1},t_{k+2}$ \\
\end{tabular}

\begin{tabular}{ll}
 \multicolumn{2}{c}{\bf Global Features} \\
 \hline
  $t^l_{i}$                     & $1 \le i < k - 1$ \\
  $t^l_{i},t^l_{i+1}$           & $1 \le i < k - 2$ \\
  $t^l_{i},t^l_{i+1},t^l_{i+2}$ & $1 \le i < k - 3$ \\
  $t^l_{i}$                     & $k \le i < n - 1$ \\
  $t^l_{i},t^l_{i+1}$           & $k \le i < n - 2$ \\
  $t^l_{i},t^l_{i+1},t^l_{i+2}$ & $k \le i < n - 3$ \\
\end{tabular}

\caption{Feature templates. $k$ is the boundary position, $t_k$ is the $k$ th POS tag (level 0), and $t^{l}_{i}$ is the $i$ th POS tag in the $l$-level POS tag sequence.}
\label{tbl:features}
\end{table}

@@

We use only part-of-speech tags to create features for the classifier
(adding lexical or other features is left to future work). The
property of independence between two words is inherently global, as it
can be affected by structure arbitrarily far away. Thus we have both
local and global features. The global features are furthermore
distinguished by \textbf{POS level}, explained in detail in the next section. The specific
feature templates are shown in Table~\ref{tbl:features}.

@@

To compare with previous work on parsing using the Penn Treebank, we show the
time and accuracy for parsing section 23, using both linear and kernel
classifier output along with the baseline parser in Table~\ref{tbl:wsj23}. The times reported are
the average of three runs each. Because there was significant variation in parse
time when multiple processes were run in parallel, for these results only one
process was run at a time. The results parallel those shown on the development
data.

\begin{table}
  \centering
\begin{tabular}{llll}
{\bf Parser} & {\bf Time} (s) & {\bf Speedup} & {\bf F$_{\text{1}}$} \\
\hline
baseline & 1538 & & 85.54 \\
linear & 1106 & 1.39\texttimes{} & 83.55 (-1.99)\\
 & (+100) & (1.28\texttimes{}) &  \\
poly & 1040 & 1.48\texttimes{} & 84.57 (-0.97)\\
\end{tabular}
\caption{Results of parsing WSJ section 23.}
\label{tbl:wsj23}
\end{table}

@@

\bibliographystyle{acl}
\bibliography{references}

\newpage
\begin{appendices}
%% \section{Appendix}
\label{sec-8}

\section{\hspace{-1em}.\hspace{.5em} Derivation of equations in section \ref{sec:comp-saved}}
\label{sec:derivation-equations}

@@

{\small
\begin{align*}
%% \begin{equation*}
%% \begin{split}
& \sum_{j=2}^{n}\sum_{i=1}^{n-j+1}\sum_{k=i+1}^{i+j-1}|G|\\
=& |G|\sum_{j=2}^{n}(n-j+1)(j-1)\\
=& |G|\sum_{i=1}^{n-1}(n-i)(i)\\
=& |G|\sum_{i=1}^{n-1}(ni - i^2)\\
=& |G|(n\sum_{i=1}^{n-1}i - \sum_{i=1}^{n-1}i^2)\\
=& |G|(n\frac{(n-1)n}{2} - (\frac{n^3}{3} - \frac{n^2}{2} + \frac{n}{6}))\\
=& |G|(\frac{1}{2}n^3 - \frac{1}{2}n^2 - \frac{1}{3}n^3 + \frac{1}{2}n^2 - \frac{1}{6}n)\\
=& |G|(\frac{1}{6}n^3 - \frac{1}{6}n)
%% \end{split}
%% \end{equation*}
\end{align*}
}

@@

{\small
\begin{equation*}
\begin{split}
& |G_{comp}|[\frac{1}{6}n^3 - \frac{1}{6}n]\\& - |G_{comp}|[\frac{1}{6}(\frac{n}{K})^3 - \frac{1}{6}\frac{n}{K}]\\& - |G_{comp}|[\frac{1}{6}(\frac{(K-1)n}{K})^3 - \frac{1}{6}\frac{(K-1)n}{K}]\\
=& |G_{comp}|[\frac{1}{6}n^3 - \frac{1}{6}n - \frac{1}{6}\frac{(K-1)^3 +1}{K^3}n^3 + \frac{1}{6}n]\\
=& |G_{comp}|[\frac{1}{6}\frac{K^3}{K^3}n^3 - \frac{1}{6}\frac{K^3 - 3K^2 + 3K}{K^3}n^3]\\
=& |G_{comp}|\frac{3K^2 - 3K}{6K^3}n^3
\end{split}
\end{equation*}
}

@@

{\small
\begin{equation*}
\frac{|G_{comp}|\frac{3K^2 - 3K}{6K^3}n^3}{|G|(\frac{1}{6}n^3 - \frac{1}{6}n)}
\end{equation*}
}

@@

{\small
\begin{equation*}
\begin{split}
& \lim_{n \to \infty}\frac{|G_{comp}|\frac{3K^2 - 3K}{6K^3}n^3}{|G|(\frac{1}{6}n^3 - \frac{1}{6}n)}\\
=& \frac{|G_{comp}|}{|G|}[\frac{3}{K} - \frac{3}{K^2}]
\end{split}
\end{equation*}
}

@@

{\small
\begin{equation*}
\begin{split}
& |G_{comp}|[\frac{1}{6}n^3 - \frac{1}{6}n]\\
& - K|G_{comp}|[\frac{1}{6}(\frac{n}{K})^3 - \frac{1}{6}\frac{n}{K}]\\
=& |G_{comp}|[\frac{1}{6}n^3 - \frac{1}{6}n - \frac{1}{6}\frac{1}{K^2}n^3 + \frac{1}{6}\frac{n}{K}]\\
=& |G_{comp}|\frac{1}{6}\frac{K^2-1}{K^2}n^3
\end{split}
\end{equation*}
}

@@

{\small
\begin{equation*}
\begin{split}
& \lim_{n \to \infty}\frac{|G_{comp}|\frac{1}{6}\frac{K^2-1}{K^2}n^3}{|G|(\frac{1}{6}n^3 - \frac{1}{6}n)}\\
=& \frac{|G_{comp}|}{|G|}\frac{K^2-1}{K^2}
\end{split}
\end{equation*}
}

@@

\section{\hspace{-1em}.\hspace{.5em} Detailed parse results}
\label{sec:parse-results-full}
\label{sec-8-2}

\end{appendices}

\end{document}
